A Survey of Wearable Device Risk Perceptions

### 2015-01-06 wearables_survey.tex
Added the two Camp references into the related work section.

Wearables are the new frontier of ubiquitous computing, with new capabilities can capture unique data about the user and his/her surroundings. As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security~\cite{palen2003unpacking}. Privacy in ubiquitous systems can be achieved by adhering to principles such as notice, choice, and consent~\cite{langheinrich2001privacy}. An example of research which aims to uphold such principles include work by Egelman \etal , which evaluates various indicator designs to better communicate data capture on ubiquitous computing platforms.

>>>>

Wearables are the new frontier of ubiquitous computing, with new capabilities can capture unique data about the user and his/her surroundings. As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security~\cite{palen2003unpacking}. This is because the internet is ubiquitous but, have characteristics of a private space~\cite{camp2000internet}. Privacy in ubiquitous systems can be achieved by  identifying subtle trust assumptions of systems for design~\cite{camp2003designing} and adhering to privacy principles~\cite{langheinrich2001privacy}. An example of research which aims to uphold such principles include work by Egelman \etal , which evaluates various indicator designs to better communicate data capture on ubiquitous computing platforms.
